Errata

### 2025-04-05 tex/Manuscript-2.tex
Refactor methodology and results sections: update chapter and section numbering, adjust labels and references, and improve table and figure captions for clarity and consistency.
Remove auxiliary files for Manuscript-4, Manuscript-5, Methodology, and Results_Discussion to clean up the repository and prevent unnecessary clutter.

@@

>>>>

\begin{center}
  \textbf{\Large Manuscript 2}

  \vspace{0.3cm}
  \textit{Geoderma}\\
  \textit{Submitted}

  \vspace{0.5cm}

  Nicolás Riveras-Muñoz\textsuperscript{1*}, Steffen Seitz\textsuperscript{1}, Corinna Gall\textsuperscript{1}, Victoria Rodríguez\textsuperscript{2}, Kristina Witzgall\textsuperscript{3}, Peter Kühn\textsuperscript{1}, Carsten W. Mueller\textsuperscript{4,5}, Rómulo Oses\textsuperscript{6}, Oscar Seguel\textsuperscript{7}, Dirk Wagner\textsuperscript{2,8}, and Thomas Scholten\textsuperscript{1}

  \vspace{0.2cm}
\end{center}

\begin{small}
  \begin{justify}

    \textsuperscript{1}University of Tübingen, Department of Geosciences, Soil Science and Geomorphology, Rümelinstr. 19–23, 72070 Tübingen, Germany

   \textsuperscript{2}GFZ Helmholtz Centre for Geosciences, Section Geomicrobiology, Telegrafenberg, 14473 Potsdam, Germany

   \textsuperscript{3}Technical University of Munich, Soil Science, Emil-Ramann-Str. 2, 85354 Freising, Germany

   \textsuperscript{4}Technische Universität Berlin, Ernst-Reuter-Platz 1, 10587 Berlin, Germany

   \textsuperscript{5}Department of Geosciences and Natural Resource Management, University of Copenhagen, Copenhagen, Denmark

   \textsuperscript{6}Universidad de Atacama, Centro Regional de Investigación y Desarrollo Sustentable de Atacama (CRIDESAT), Copayapu 485, Copiapó, Chile

   \textsuperscript{7}Universidad de Chile, Facultad de Ciencias Agronómicas, Av. Santa Rosa #11315, La Pintana, 8820808 Santiago, Chile

   \textsuperscript{8}University of Potsdam, Institute of Geosciences, Karl-Liebknecht-Str. 24-25, 14476 Potsdam, Germany

  \end{justify}
\end{small}

\vspace{0.5cm}
\begin{center}
  Submitted: March 17, 2025\\
\end{center}
\cleardoublepage

@@

\bibliographystyle{apalike}
\bibliography{literatur}
